A Visibility-Based Combinatorial Data Structure for Mobile Robots in Polygons

### 2018-05-17 final_paper/paper.tex
all sections filled out

\begin{figure}
\centering
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=0.6\linewidth]{images/concave_pent.png}
  \label{fig:c_p}
\end{subfigure}
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=0.8\linewidth]{images/viz_edge_graph.png}
\end{subfigure}
\caption{The vertex-edge visibility graph for the polygon in Fig
\ref{fig:c_p}\label{fig:veg}}

@@

The link diagram, as introduced in \cite{tan_sweep}, displays the link distance between any two points on the boundary of the polygon. \textcolor{red}{Do we need to create our own picture for link diagram here} The link diagram is our main motivation for creating a visibility diagram augmented with bouncing information.
\begin{figure}
    \includegraphics[width=0.6\linewidth]{images/link_distance.png}
    \centering
    \caption{The link distance between $v_1$ and $v_2$ is 3, as shown by the three blue line segments connecting the two vertices.}\label{fig:link_dis}
    \centering
\end{figure}

@@

\centering
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.7\linewidth]{images/color_pent.png}
\label{fig:color_pent}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.8\linewidth]{images/bvd.png}
\end{subfigure}
\caption{The bounce visibility diagram for the polygon shown in Fig~\ref{fig:color_pent}. }
\label{fig:bvd}

@@

\begin{figure}
% \makebox[\linewidth][c]{%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.5\linewidth]{images/regular_pent.png}
\end{subfigure}
\begin{subfigure}{0.25\textwidth}
\includegraphics[width=0.8\linewidth]{images/regular_pent_bvd.png}
\end{subfigure}
\centering
% }\\
\caption{The bounce visibility diagram for the regular pentagon. }
\label{fig:regular_pent_bvd}
\end{figure}

We can easily extract information for the fixed angle bouncing strategy
mentioned in section \ref{subsec:bounce_strategy} by overlaying an horizontal
line $\theta = \theta_0$ onto the BVD, where $\theta_0$ is the angle chosen by
the bouncing strategy. In Fig \ref{fig:limit_cycle_bvd}, one of the possible
limit cycle with fixed angle $\theta = 0.6$ for the concave quadrilateral is
shown in Fig \ref{fig:limit_cycle}; the bounce visibility diagram for this
polygon is shown in Fig \ref{fig:concave_quad_bvd} with the horizontal line
$\theta = \theta_0$, where $\theta_0 = \frac{\pi}{2}-0.6$ (we need to convert
the angle from w.r.t the normal of the wall to w.r.t the forward direction of
the robot). The horizontal line cut through different regions of the diagram,
representing the possible edges that the robot can bounce to at different points
on the boundary with bounce angle $\theta_0$. For example, at edge $v_5v_0$, the
robot can bounce to edge $v_0v_1$ and $v_1v_2$. We can create a graph for
$\theta = \theta_0$, whose nodes are edges in $P'$ and two nodes are connected
by a directed edge if the robot can bounce from one edge to another at
$\theta_0$, as shown in Fig \ref{fig:limit_cycle_diagram}. It is more stable
for the robot to bounce to some edges than others. In the diagram
(Fig \ref{fig:concave_quad_bvd}), the line $\theta = \theta_0$ cuts through
four different regions for $x \in (2, 3)$, but the sections for $v_4v_5$ and
$v_0v_5$ are much larger than those for $v_0v_1$ and $v_1v_2$. So we know it is
more likely and more stable for the robot to bounce to edge $v_4v_5$ and
$v_0v_5$. We marked the edge with unstable bounce in the graph with $\omega$ in
Fig \ref{fig:limit_cycle_diagram}. The limit cycle shown in
Fig \ref{fig:limit_cycle} corresponds to the cycle
$v_0v_1\rightarrow v_3v_4\rightarrow v_4v_5 \rightarrow v_1v_2 \rightarrow v_2v_3 \rightarrow v_0v_5 \rightarrow v_0v_1$
in Fig \ref{fig:limit_cycle_diagram}.
(\textcolor{red}{do we talk about this here or later in the task})

@@

\section{BVD as an Information Space}

@@

@@

@@

\subsection{Augmenting the Diagram with Dynamical Information}

\begin{itemize}
\item Laser Beams - laser beams form new, internal edges of the polygon. They can be added to the bounce visibility graph by marking all the edges which represent bounces that would cross the laser beam with a special symbol. different symbols for distinguishable beams. If beam is encountered, only propagate state estimate forward along edges with that symbol. To guarantee reduction in uncertainty, put laser beams in positions that break graph symmetry {\color{red} flesh out this idea}
\item Pebbles
\item Cameras
\end{itemize}

@@

If the start set $S$ is such that it is equal to one of the equivalence
classes of the data structure, a navigation query is simple - the start set in
the graph is a single node, and the query is solved by a shortest path from this
node to the nodes representing the goal set. The shortest path will correspond
to the navigation strategy with the fewest number of bounces.

@@

In prior work {\color{red} cite}, it was shown that stable limit cycles exist for fixed bouncing in regular polygons, for some ranges of bounce angles. These results also hold for convex polygons in general.

- sketch main idea: contraction mapping from one edge back to itself -> fixed point on edge -> limit cycle

What about nonconvex polygons?

- easy case: choose subset of edges that, if extended to their intersections, form convex polyon

- harder case: choose periodic sequence of sequentially visible edges

- trickiness of composing functions: range of angles which lead to limit cycle must be supported by every range/domain along compositional chain

- complexity of this search: all cycles in graph?

@@

incorporate "Localization with Limited Sensing"

\section{Toward a Hierarchy of Bouncing Robots}

@@

randomized plans?

\section{Conclusion}

>>>>

\begin{figure}
\centering
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=0.6\linewidth]{images/concave_pent.png}
  \label{fig:c_p}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=0.8\linewidth]{images/viz_edge_graph.png}
\end{subfigure}
\caption{A polygon and its corresponding vertex-edge visibility graph.\label{fig:veg}}

@@

The link diagram, as introduced in \cite{tan_sweep}, displays the link distance between any two points on the boundary of the polygon. The link diagram is our main motivation for creating a visibility diagram augmented with bouncing information.
\begin{figure}
    \includegraphics[width=0.6\linewidth]{images/link_distance.png}
    \centering
    \caption{The link distance between $v_1$ and $v_2$ is 3, as shown by the three blue line segments connecting the two vertices.}\label{fig:link_dis}
    \centering
\end{figure}

@@

\centering
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.7\linewidth]{images/color_pent.png}
\captionof{figure}{\label{fig:color_pent}}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.8\linewidth]{images/bvd.png}
\end{subfigure}
\caption{A polygon and its corresponding bounce visibility diagram.}
\label{fig:bvd}
\end{figure}

@@

\begin{figure}
% \makebox[\linewidth][c]{%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.5\linewidth]{images/regular_pent.png}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.8\linewidth]{images/regular_pent_bvd.png}
\end{subfigure}
% }\\
\caption{The bounce visibility diagram for the regular pentagon. }
\label{fig:regular_pent_bvd}
\end{figure}

@@

\section{BVD as an Information Space \label{bvd_info}}

@@

\subsection{Augmenting the Graph with Dynamical Information}

@@

Furthermore, the contraction property of a composition of multiple bounces can
be determined by simply multiplying the coefficients $\frac{\sin(\theta_i -
\phi_i)}{\sin(\pi-\theta_i)}$, and the constraints on the satisfying angles
$\theta_i$ can be propagated through the composition.

@@

\subsection{Sensor Modelling}

Here we sketch how different virtual sensors may be incorporated into this
information space representation.

\begin{itemize}
\item \emph{Laser Beams:} laser beams form new, internal edges of the polygon. They can be
added to the bounce visibility graph by marking all the edges which represent
bounces that would cross the laser beam with a special symbol. different symbols
for distinguishable beams. If a beam is encountered, and we are tracking state
as a set of possible segments along the boundary of $P'$, we can reduce
uncertainty in our estimate by only propagating the state estimate
forward along edges with that symbol. To engineer reduction in uncertainty,
we may be able to put laser beams in positions that break graph symmetry.
\item \emph{Pebbles:} pebbles are quite important in many robotic tasks, such as
when we need to guarantee that a wall-following strategy has successfully
circumnavigated a polygon. In this representation, we can simply augment nodes
in $G_{BVE}$ if our robot has placed a pebble in that segment (or we may mark
multiple nodes, then use actions to reduce uncertainty in our state estimate
once we return to the pebble).
\item \emph{Cameras:} Especially when discussing coverage, it is helpful to have
some sense of how we "cover" a polygon's interior. One abstract sensor with this
behavior is a model of a camera, which may have some given range and field of
view. The set-theoretic representation of this visibility region can be used to
represent how much of the polygon may be covered by a given trajectory. Ideally,
coverage strategies would allow for satisfying coverage given nondeterminism in
the start states and actions.
\end{itemize}

@@

If the start set $S$ is such that it is equal to one of the equivalence
classes of the data structure, a navigation query is simple - the start set in
the graph is a single node, and the query is solved by a shortest path from this
node to the nodes representing the goal set. The shortest path will correspond
to the navigation strategy with the fewest number of bounces. It would also be
possible to determine the shortest path in the metric space of the polygonal
environment, either by adding weights to the edges in the graph, or by
leveraging results from shortest path navigation using visibility diagrams.

@@

We define the \emph{patrolling} task as:

\begin{quotation}
Given an accurate map of the environment, a set of possible starting states, and
a sequence of edges of the environment,
determine a strategy which causes the robot to visit each edge of the sequence
in order on a repeatable path.
\end{quotation}

This task is related to the Aquarium Keeper's Problem in computational
geometry \cite{czyzowicz1991aquarium}.

In prior work \cite{nilles2017periodic}, it was shown that stable limit cycles
exist for constant-angle fixed bouncing in regular polygons, for some ranges of bounce angles.
These results also hold for convex polygons in general.

The general flavor of these results are that the bounce functions from edge to
edge are composed into one function which returns the robot to its starting
edge. If this function is a contraction map, a fixed point exists on the
starting edge, and thus a limit cycle of the robot's trajectory exists. The
exact conditions of the existence of this limit cycle depend on the product of
the contraction coefficients being less than one; and on $\theta$ being such
that the bounce at each stage can actually occur. All of the information
necessary to check these conditions is in $G_{BVD}$, as described in Section
\ref{bvd_info}.

Thus, finding all possible limit cycles in an environment $P$ amounts to finding
all cycles in $G_{BVD}$ such that this condition holds.

To examine the behavior of a robot with a given fixed bounce angle, such as the
analysis in \cite{erickson2013toward}, we can easily extract information for the fixed angle bouncing strategy
mentioned in section \ref{subsec:bounce_strategy} by overlaying an horizontal
line $\theta = \theta_0$ onto the BVD, where $\theta_0$ is the angle chosen by
the bouncing strategy. In Fig \ref{fig:limit_cycle_bvd}, one of the possible
limit cycle with fixed angle $\theta = 0.6$ for the concave quadrilateral is
shown in Fig \ref{fig:limit_cycle}; the bounce visibility diagram for this
polygon is shown in Fig \ref{fig:concave_quad_bvd} with the horizontal line
$\theta = \theta_0$, where $\theta_0 = \frac{\pi}{2}-0.6$ (we need to convert
the angle from w.r.t the normal of the wall to w.r.t the forward direction of
the robot). The horizontal line cut through different regions of the diagram,
representing the possible edges that the robot can bounce to at different points
on the boundary with bounce angle $\theta_0$. For example, at edge $v_5v_0$, the
robot can bounce to edge $v_0v_1$ and $v_1v_2$. We can create a graph for
$\theta = \theta_0$, whose nodes are edges in $P'$ and two nodes are connected
by a directed edge if the robot can bounce from one edge to another at
$\theta_0$, as shown in Fig \ref{fig:limit_cycle_diagram}. It is more stable
for the robot to bounce to some edges than others. In the diagram
(Fig \ref{fig:concave_quad_bvd}), the line $\theta = \theta_0$ cuts through
four different regions for $x \in (2, 3)$, but the sections for $v_4v_5$ and
$v_0v_5$ are much larger than those for $v_0v_1$ and $v_1v_2$. So we know it is
more likely and more stable for the robot to bounce to edge $v_4v_5$ and
$v_0v_5$. We marked the edge with unstable bounce in the graph with $\omega$ in
Fig \ref{fig:limit_cycle_diagram}. The limit cycle shown in
Fig \ref{fig:limit_cycle} corresponds to the cycle
$v_0v_1\rightarrow v_3v_4\rightarrow v_4v_5 \rightarrow v_1v_2 \rightarrow v_2v_3 \rightarrow v_0v_5 \rightarrow v_0v_1$
in Fig \ref{fig:limit_cycle_diagram}.

@@

We define the \emph{localization} task as:

\begin{quotation}
Given an accurate map of the environment, but no knowledge of configuration,
determine a strategy which eliminates uncertainty in configuration as much as
possible (ideally, to a point in configuration space).
\end{quotation}

In \cite{o2007localization}, the authors show that localization is possible with
mobile robots with a linear and angular odometer, or a compass and contact
sensor, but not with robots with only an angular odometer and contact sensor.
These sensing configurations correspond to which types of bounce laws each robot
is capable of performing, and we would like to be able to rederive the same
results in this representation.

Localization amounts to a path finding algorithm in the larger graph, where each
node is an element of the powerset of segments along $P'$. Future work will
include how to tractibly search this graph (such as heuristics for doing so
which take advantage of the uncertainty-reducing properties of contraction
mappings).

@@

Future work also includes:

\begin{itemize}
\item Characterizing the completeness and correctness of algorithms for
navigation, coverage, localization, etc.
\item Continue to place this work in context, especially with BitBots, Gap
Navigation Trees, and Combinatorial Visibility Vectors
\item Developing ways to query two $G_{BVD}$s, generated with different constraints on
 bouncing laws and sensors, and determine whether one represents a robot which
is ``more powerful" than another. Perhaps this will require a clever
parameterization of bouncing laws.
\item Investigate how to generate bounce law distributions that allow a bounce
to be randomly selected at each stage and guarantee some properties about the
resulting trajectory
\item Extending analysis to more tasks, such as coverage and pursuit-evasion
\end{itemize}
